---
title: "Final Project"
author: "Hui Jing"
date: "12/6/2019"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
#  install.packages("boot")
#  install.packages("simpleboot")
# install.packages("wBoot")
# 
# 
#  install.packages("caret")
#  install.packages("caTools")
#  install.packages("glmnet")
#  install.packages("mlbench")
#  install.packages("psych")
#  install.packages("ggplot2")
#  install.packages("ggthemes")
#  install.packages("dplyr")
#  install.packages("corrplot")
#  install.packages("corrgram")
#  install.packages("tidyr")
#  install.packages("magrittr")
#  install.packages("gridExtra")
#  install.packages("rcompanion")
```


## data prepareation 
```{r}



library(boot)
library(simpleboot)
library(wBoot)

library(caret)
library(caTools)
library(glmnet)
library(mlbench)
library(psych)
library(ggplot2)
library(ggthemes)
library(dplyr)
library(corrplot)
library(corrgram)
library(tidyr)  
library(magrittr)       
library(gridExtra) 
library(rcompanion)
```

```{r}


dataset <- read.csv(file="C:/Users/onepi/Documents/NEU/IE6200/final project/20191002-items.csv", header=TRUE, sep=",")
set.seed(1315)
#Exploring DataSet
head(dataset)
#printing all columns with their data type
str(dataset)
#Checking Null values
any(is.na(dataset))

#data Preparation
#Dropping the url,date and itemID for EDA
data <- dataset[c(2,3,4,6,7,8)]
# EDA can be analyzed below
# you can see the categoricql variables and their sub categories along with their frequencies 
# for numerical variables you can see the different corresponding statistical parameter's values
summary(data)

```


```{r}




#finding correlation between numeric values
num.cols <- sapply(dataset,is.numeric)
#finding correlation between numeric values
cor.data <- cor(dataset[,num.cols])
#visualizing correlation 
print(corrplot(cor.data , method = "color"))


```



```{r}
options(scipen = 999)
pairs.panels(data)

```




## Introducation 




## Visualation 


```{r}
slices <-c(4422,701,1290,3318,1211)
category<-c("beli-harddisk-eksternal","beli-laptop","beli-smart-tv","jual-flash-drives","shop-televisi-digital")
pie(slices, labels = category, main="Pie Chart of Categories")
```
```{r}
my_data <- data[ which(data$price <=3020219), ]

boxplot(price~category , data = my_data, col="red", varwidth=TRUE, notch=FALSE, 
        las=1, main="Average Price according to Category",cex.axis=0.6)

```


```{r}
my_data= data[(data$category == "beli-harddisk-eksternal") | (data$category == "beli-laptop") | (data$category == "beli-smart-tv") | 
                (data$category == "jual-flash-drives") | (data$category == "shop-televisi-digital"), ]
par(mfcol=c(3,2))
colors = c("red", "yellow", "green", "violet", "orange") 
hist(my_data[(data$category == "beli-harddisk-eksternal"),]$price,main='beli-harddisk-eksternal',xlab='Average Price', ylab='Frequency',col=colors)
hist(my_data[(data$category == "beli-laptop"),]$price,main='beli-laptop',xlab='Average Price', ylab='Frequency',col=colors)
hist(my_data[(data$category == "beli-smart-tv"),]$price,main='beli-smart-tv',xlab='Average Price', ylab='Frequency',col=colors)
hist(my_data[(data$category == "jual-flash-drives"),]$price,main='jual-flash-drives',xlab='Average Price', ylab='Frequency',col=colors)
hist(my_data[(data$category == "shop-televisi-digital"),]$price,main='shop-televisi-digital',xlab='Average Price', ylab='Frequency',col=colors)

```

##### The price summary

```{r}
head(data$price, 10)
summary(data$price, 10)
```





```{r}


options(scipen = 999)
g1 <- ggplot(data, aes(price)) + geom_histogram(fill = "green",bins = 20 , color = "grey30")


#scaling
g2 <- ggplot(data, aes(price)) + geom_histogram(fill = "blue",bins = 20 , color = "grey30") + scale_x_log10()
grid.arrange(g1, g2,ncol = 1)


```




```{r}
# data$price <-((order(data$price)))
# quantile(data$price)
# plotNormalHistogram(data$price)
```


```{r}
qqnorm(data$price)
qqline(data$price, col="red")
```

```{r}
quantile(data$price, seq(.01, .99, .1))
x_bar <- mean(data$price)
x_bar
```


## Stat Test
### One sample t-test 
####(a) traditional statistical tools


```{r}
t.test(data$price, mu = 3020219, alternative = "greater")
```

####(b) using Bootstraping1

```{r}
boot.one.bca(data$price,mean , null.hyp = NULL,
             alternative = c("greater"),
             conf.level = 0.95, type = NULL, R = 9999)
```





  
  mean price of flash drive 
  
### one sample test of proportion H0

####(a) traditional statistical tools  

```{r}
#Categorial variable of interest with 2 categories is aplicable for One sample propotion test
#We have a categorical variable with five categories but we can recode it so that instead of all five i.e
#1.beli-harddisk-eksternal 
#2.beli-laptop
#3.beli-smart-tv 
#4.jual-flash-drives
#5.shop-televisi-digital
#we have shop-televisi-digital and not shop-televisi-digital.
table(data$price,data$category)

binom.test( x = 6800 , n = 10942, p = 0.4, alternative="greater")

```

####(b) using Bootstraping  

```{r}
shop.televisi.digital <- factor(rep(c("shop-televisi-digital", "other"), c(4422, 10942-4422)))
table(shop.televisi.digital)
plot(shop.televisi.digital)


shop.televisi.digital <- rep(c(1, 0), c(4422, 10942-4422))
num_sims <- 10000
# A vector to store my results
results <- rep(NA, num_sims)
# A loop for completing the simulation
for(i in 1:num_sims){
  results[i] <- mean(sample(x = shop.televisi.digital,
                            size = 10942,
                            replace = TRUE))
}
# Finally plot the results
hist(results,
     freq = FALSE, 
     main ='Sampling Distribution of the Sample Proportion under H_0:p=0.4', 
     xlab = 'Proportion of shop.televisi.digital', ylab = 'Density')
# estimate a normal curve over it - this looks pretty good!
lines(x = seq(.35, .65, .001), dnorm(seq(.35, .65, .001), mean = mean(results), sd = sd
                                     (results)))
abline(v=.41, col="red")

count_of_more_extreme_upper_tail <- sum(results >= .4)
bootstrap_pvalue <- count_of_more_extreme_upper_tail/num_sims
bootstrap_pvalue
cat("Exact Binomial p-value")
## Exact Binomial p-value
binom.test(x=6800, n = 10942, p=(.6), alternative="greater")$p.value
cat("Normal Approximation p-value")
## Normal Approximation p-value
pnorm(0.4, lower.tail = FALSE)
```

  

  
### two sample t-test for difference in means
####(a) traditional statistical tools

```{r}


data$category <- factor(rep(c("shop-televisi-digital", "other"), c(4422, 10942-4422)))

x_bar_n <- mean(data$price[data$category=="shop-televisi-digital"])
x_bar_s <- mean(data$price[data$category=="other"])
# null hypothesized population mean difference between the two groups
mu_0 <- 0
# sample variances
s_n_sq <- sd(data$price[data$category=="shop-televisi-digital"])**2
s_s_sq <- sd(data$price[data$category=="other"])**2
# sample size
n_n <- length(data$price[data$category=="shop-televisi-digital"])
n_s <- length(data$price[data$category=="other"])
# t-test test statistic
t <- (x_bar_n - x_bar_s - mu_0)/sqrt((s_n_sq/n_n) + (s_s_sq/n_s))

x_bar_n

(x_bar_n-x_bar_s)+(qt(0.25, min(n_n, n_s)-1)*sqrt((s_n_sq/n_n) + (s_s_sq/n_s)))

(x_bar_n-x_bar_s)+(qt(0.75, min(n_n, n_s)-1)*sqrt((s_n_sq/n_n) + (s_s_sq/n_s)))

t.test((data$price[data$category=="shop-televisi-digital"]), (data$price[data$category=="other"]))


```

####(b) Bootstrapping Method

```{r}

r <- data$price[data$category=="shop-televisi-digital"]
c <- data$price[data$category=="other"]


boot.paired.bca(r, c, null.hyp = NULL,
                alternative = c("two.sided"),
                conf.level = 0.95, type = NULL, R = 9999)
```

### two sample test for difference in proportions 

  two brand flash drive has same proportion sales in thier brand 
####(a) traditional statistical tools

```{r}

prop.test(c(6520,40),c(44220,120),correct=FALSE)
```

####(b) Bootstrapping Method

```{r}

shop.televisi.digital <- factor(rep(c("shop-televisi-digital", "other"), c(4422, 10942-4422)))
table(shop.televisi.digital)

shop.televisi.digital <- rep(c(1, 0), c(4422, 10942-4422))
table(shop.televisi.digital )

shop.televisi.digital[0]

boot.two.per(data$price,shop.televisi.digital,mean, stacked = TRUE, variable = data,
             null.hyp = NULL, alternative = c("two.sided"),
             conf.level = 0.95, type = NULL, R = 9999)

```

  
### Chi-square 
####a) traditional statistical tools  
  The number of sales for  each brand in flash drive 
  
```{r}

#It compares multiple observed proportions to expected probabilities. 

set.seed(0)
data("dataset$cate")
head(dataset$category)

# x <- c(1963 ,3394 ,7627 ,8857 ,9439)
# x <- c(55800, 2499000, 1275000, 3850000, 3984100, 3788000)
#probability of above samples are
table(dataset$category)
prop.table(table(dataset$category))
sum(((table(dataset$category) - 10492*0.2)^2)/10492*0.2)
# prop.table(table(data))

# collected some random sample price for Chi-square goodness of fit test
#Assuming each of the class in category have same proportion
pchisq(195.9637, df = 5-1, lower.tail = FALSE)
# chi <- chisq.test(x, p = c(1/6, 1/6, 1/6, 1/6 ,1/6,1/6 ))
# chi

```




  

## Appendix


```{r ref.label=knitr::all_labels(), echo = T, eval = F}
```

